### 2017-06-14 06-conclusion.tex
Typos in conclusion

We further created a highly scalable implementation to handle the largest existing
community graphs on a distributed cluster machine. The most important data structures
are partitioned across the collective memory of the cluster nodes, which
significantly increases data access latency for our already data-dominant algorithm.
We made several contributions to improve performance and still maintain scalabitiy:
we created a custom distributed Key-Value store implemented with high-speed RDMA
primitives that exploits the algorithm's structure to avoid concurrency issues; we
use MPI for synchronization and work distribution between the master and worker nodes;
and
we overlapped computation
with communication to hide latency.
%
By evaluating the system empirically using 65 cluster nodes and large data sets,
we show that its strong and weak scalability are both good. We also compared its
performance against a 40-core shared-memory system with 1TB of memory.
The distributed system has far stronger performance because it has more cores and
more collective memory bandwidth, even though it must fetch its data through the network.
% Additionally, we assessed the efficiency of the algorithm's resource utilization.
Finally, a
demonstration of the implementation's utility was provided by processing 6
large real-world data sets.
To the best of
our knowledge, this is the first time that the problem of deducing overlapping
communities has been learned for problems of such a large scale.

>>>>

We further created a highly scalable implementation to handle the largest existing
community graphs on a distributed cluster machine. The most important data structures
are partitioned across the collective memory of the cluster nodes, which
significantly hurts data access latency and bandwidth for our already data-dominant algorithm.
We made several contributions to improve performance and still maintain scalability:
we created a custom distributed Key-Value store implemented with high-speed RDMA
primitives, that exploits the algorithm's structure to avoid concurrency issues; we
use MPI for synchronization and work distribution between the master and worker nodes;
and
we overlapped computation
with communication to hide latency.
%
By evaluating the system empirically using 65 cluster nodes and large data sets,
we show that its strong and weak scalability are both good. We also compared its
performance against a 40-core shared-memory system with 1TB of memory.
The distributed system has far stronger performance because it has more cores and
more collective memory bandwidth, even though it must fetch its data through the network.
% Additionally, we assessed the efficiency of the algorithm's resource utilization.
Finally, a
demonstration of the implementation's utility was provided by processing 6
large real-world data sets.
To the best of
our knowledge, this is the first time that the problem of deducing overlapping
communities has been learned for problems of such a large scale.
